Accessible, realistic genome simulation with selection using \stdpopsim

### 2025-03-19 analysis2_manuscript.tex
Update analysis2_manuscript.tex
Co-authored-by: Andrew Kern <adkern@uoregon.edu>

    Overall, inferred DFEs varied across populations and inference methods (Figure \ref{fig:homsap-dfe.ooa}). %, Table \ref{tab:dfe_table}). IG: Table seems less relevant here
    Note that while the estimation accuracy for the DFE parameters themselves is informative (Figure \ref{fig:homsap-dfe.ooa}A-B),
    examining the difference between the actual and inferred distributions of $s$ can be more helpful for showing how well a method
    has recovered the true DFE (Figure \ref{fig:homsap-dfe.ooa}C).
    The distributions of $s$ inferred by \polydfe and \dadicli had higher mean values (in absolute value)
    but smaller shape parameters, while \grapes inferred distributions with lower mean values and shape parameters.
    As a result, \polydfe and \dadicli over-estimate the fraction of mutations under strong selection ($s<-0.1$),
    while \grapes considerably over-estimates the fraction of mutations under weak selection ($s\geq-0.0001$).

>>>>

    Overall, inferred DFEs varied across populations and inference methods (Figure \ref{fig:homsap-dfe.ooa}, Table \ref{tab:dfe_table}). 
    Note that while the estimation accuracy for the DFE parameters themselves is informative (Figure \ref{fig:homsap-dfe.ooa}A-B),
    examining the difference between the actual and inferred distributions of $s$ can be more helpful for showing how well a method
    has recovered the true DFE (Figure \ref{fig:homsap-dfe.ooa}C).
    The distributions of $s$ inferred by \polydfe and \dadicli had higher mean values (in absolute value)
    but smaller shape parameters, while \grapes inferred distributions with lower mean values and shape parameters.
    As a result, \polydfe and \dadicli over-estimate the fraction of mutations under strong selection ($s<-0.1$),
    while \grapes considerably over-estimates the fraction of mutations under weak selection ($s\geq-0.0001$).
